---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(janitor)
library(broom)
library(ggfortify)
```

```{r}
projects <- read_csv("week_10_hw_data/project_management.csv") %>% select(-X1)
```

```{r}
projects %>% 
ggplot(aes(y = actual_length, x = estimated_length)) +
  geom_point()
```

```{r}
projects %>% 
  summarise(cor(actual_length, estimated_length))

```

As the r value is 0.805, it is very close to 1 and therefore indicates a strong correlation between actual job length and the estimated job time i.e as the the longer jobs were also esitmated to take longer.



```{r}
model <- lm(actual_length ~ estimated_length, data = projects)

model

summary(model)
```

actual_length(^) = y(Intercept) + m * estimated_length(x)

As the gradient is 1.2235 we can see that for every 1 day of estimated_length, actual length increases by 1.2235 days 

As r^2 is 0.6475, that says that the model can predict 65% of the variation in actual length can be predicted from the variation in estimated_length

```{r}
tidy(model)

clean_names(glance(model))



autoplot(model)

projects %>% 
  add_residuals(model)
```

As the P value is < 0.05 we can reject the null hypothysis and say that there is a correlation between the estimated time and actual time of jobs.