---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
movies_data <- read_csv("data/movies.csv")
```
Question 1
What could be investigated:
- Revenue compared to budget
- How many films made/lost money 
- How many films kept their origianl titles 
- If run time affects vote average
- If a higher vote count = a higher vote average 
- Turn any 0 in budget or revenue into NAs

Mandy's answers :-

- There are a lot of NAs in homepage and tagline columns
- How much will be lost if we get rid of all the rows with NAs

```{r}
#Question 2
movies_selected <- movies_data %>% 
  select(title, runtime, budget)

movies_selected
```
```{r}

#Question 3
movies_selected %>% 
  summarise(na_runtime = sum(is.na(runtime)),
            na_title = sum(is.na(title)),
            na_budget = sum(is.na(budget)))

# run for each column or...(more for analysis rather than data wrangling)
colSums(is.na(movies_selected))

# Mandy's answer

movies_selected %>% 
  summarise(across(.fns = ~sum(is.na(.x))))
```

```{r}
# Question 4
movies_runtime <- movies_selected %>% 
  mutate(runtime = na_if(runtime, 0)) %>% 
  arrange(runtime)

movies_runtime

colSums(is.na(movies_runtime))
```

```{r}
# Question 5
movies_imputed <-  movies_runtime %>%
  mutate(runtime = coalesce(runtime, 
                            median(runtime, na.rm = TRUE)))
                           
colSums(is.na(movies_imputed))
```

```{r}
# Question 6
movies_imputed %>% 
  slice_max(runtime, n = 10)

movies_imputed %>% 
  slice_min(runtime, n = 10)

```


```{r}
# Question 7
movies_imputed <- movies_selected %>%
  mutate(budget = if_else(budget <= 100, median(budget), budget)) %>% 
  mutate(runtime = na_if(runtime, 0)) %>% 
  mutate(runtime = coalesce(runtime, 
                            median(runtime, na.rm = TRUE)))
movies_imputed
  
```
# Extension

```{r}
movie_budget <- movies_data %>% 
  select(budget) %>% 
  mutate(budget_type = case_when(
    budget < 12e6 ~ "small budget", 
    budget < 40e6 ~ "medium budget",
    budget >= 40e6 ~ "big budget"
  )
)

movie_budget
```
```{r}
# 2nd extension question - Check the homework folder for answer
movies_data %>% 
  summarise(across(
    .cols = where(is.numeric),
    .fns = ~sum(is.na(.x)
                )
    ))

movies_data %>% 

```

