---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

2.1 Question 1
We are going to use a dataset on house sales in Ames, Iowa over a number of years. We will be interested in the SalePrice of houses (though we should clean_names() the data, so this will end up as sale_price). Load the data and explore it.
```{r}
homes <- read_csv("data/ames.csv") %>% 
  clean_names()
```
2.2 Question 2
Plot a histogram of sale_price. Is the distribution normal? - No it is not, its right skewed.
```{r}
homes %>% 
  ggplot(aes(x = sale_price)) +
  geom_histogram()
```
2.3 Question 3
Calculate the population parameter mean of sale_price. Store it in a variable, as we’ll need this value later when we check if each CI contains the parameter value or not.
```{r} 
# Population parameter ------------

pop_prams <- homes %>% 
  summarise(
    mean_sale_price = mean(sale_price)
  )
```

2.4 Question 4
```{r}
results <- tibble()
for (sample_num in 1:1000){
  
  this_sample <- homes %>% 
    rep_sample_n(size = 100, replace = FALSE)
  
  this_bootstrap <- this_sample %>% 
    specify(response = sale_price) %>% 
    generate(reps = 1000, type = "bootstrap") %>% 
    calculate(stat = "mean")
  
  bootstrap_cl <- this_bootstrap %>% 
    get_confidence_interval(level = 0.95, type = "percentile")
  
  this_result <- c(
    sample_num = sample_num,
    lower = bootstrap_cl %>% 
      pull(lower_ci),
    upper = bootstrap_cl %>% 
      pull(upper_ci)
)
  
  results <- results %>% 
    bind_rows(this_result)
  
}
```

Question 5
```{r}

results %>% 
  mutate(popn_pararm_in_ci = case_when(
    pop_prams$mean_sale_price >= lower & pop_prams$mean_sale_price <= upper ~ TRUE,
    TRUE ~ FALSE)
  ) 


```
Question 6
```{r}
results %>% 
  mutate(popn_pararm_in_ci = case_when(
    pop_prams$mean_sale_price >= lower & pop_prams$mean_sale_price <= upper ~ TRUE,
    TRUE ~ FALSE)
  ) %>% 
  summarise(
    prop_in_ci = mean(popn_pararm_in_ci == TRUE)
  )
```

