---
title: "R Notebook"
output: html_notebook
---
Question 1.1.3: 3

H0 = µsleep_total(omni) - µsleep_total(herbi) = 0 
HA = Msleep_total(omni) - µsleep_total(herbi) > 0 

alpha = 0.05

```{r}
library(tidyverse)
library(ggplot2)
library(infer)


sleep <- msleep

omni_herbi <- sleep %>% 
  filter(vore == "omni" | vore == "herbi")



omni_herbi %>% 
  group_by(vore) %>% 
  summarise(average_sleep = mean(sleep_total))

omni_herbi %>% 
  ggplot(aes(y = sleep_total, x = vore)) +
  geom_boxplot()
  
```
Can see from the box plot that that it is unlikely that the difference in average sleep between vores is unlikely to be statiscally significant.

```{r}
null_distribution <- 
  omni_herbi %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 5000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_distribution %>% 
  visualise(bins = 20)


oberserved_stat <- omni_herbi %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_distribution %>% 
  visualise(bins = 20) +
  shade_p_value(obs_stat = oberserved_stat, direction = "right")

null_distribution %>% 
  get_p_value(obs_stat = oberserved_stat, direction = "right")


```
P > 0.05, we cannot reject the null hypothesis and therefore do not have the evidence to suggest the average sleep of omni and herbivores is not statistically different

Question 1.1.4 : 4
```{r}
domesdicated <- sleep %>%
  filter(!is.na(conservation)) %>% 
  mutate(is_domesticated = 
           case_when(
             conservation == "domesticated" ~ TRUE,
             TRUE ~ FALSE
           ))

oberserved_stat <- domesdicated %>% 
  specify(response =  )
```


























Question 1.2.5

With a p value of 0.07 we cannot reject the H0 hypothesis and therefore cannot conclude that 40% or more people in the town have heard of the coffee shop.

1.2.6



