---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
```
Question 1: If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
rolldie(1)

4/6
```
Question 2: How many outcomes are there in the sample space of an experiment in which we toss three dice?

size_S = 6*6*6

Question 3: In an experiment where we roll four dice:

i. how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
ii. what is the probability of this event?
iii. what assumptions do we apply in answering part ii?

```{r}
four_roll <- rolldie(4) %>% 
  mutate(total = rowSums(.)) 

dim(four_roll)

five_6_7 <- rolldie(4) %>% 
  mutate(total = rowSums(.)) %>% 
  filter(total == 5 | total == 6 | total == 7)

dim(five_6_7)

34/1296

```
Question 4 Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?
```{r}
heights <- c(1.20, 1.30, 1.4, 1.5, 1.6)

height_orders <- permutations(
  n = 5,
  r = 5,
  v = heights
)

1/120
```
5. I roll six dice:

i. what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
ii. what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
```{r}
six_dice <- rolldie(6)

six_dice %>% 
  dplyr::filter(isin(., c(6, 5, 4, 3, 2, 1)), ordered = TRUE)

1/46656

720/46656
```
Question 6

```{r}
black_cards <- cards() %>% 
  mutate(
    blacks = case_when(
      suit == "Spade" ~ TRUE,
      suit == "Club" ~ TRUE,
      TRUE           ~ FALSE
      )
  )

probability of picked a spade is 1/2
```

Question 7
```{r}
patients <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna", "Henry")

patients_ordered <- as_tibble(permutations(
  n = 8,
  r = 5,
  v = patients
))

as_tibble(patients_ordered)

patients_ordered %>% 
  dplyr::filter(isin(., c("Gianna", "Dinesh"), ordered = TRUE))

2400/6720

1200/6720
```


